Mans not hot, Man can never be hot

### 2018-01-16 article/ms.tex
observ/target section

In our research we analysed 272 Barium canidates amoung the 454,180 stellar sample produced by \citet{ho2017} and with GAIA determined the galactic motions for 21 out the 272 canidates.

\section{Observations, Target Selection}
The low-resolution spectra of our stars were obtained from the \textit{Cannon} fits predictive model implemented by \citet{ho2017} on the LAMOST (Large Sky Area Multi-Object Fibre Spectroscopic Telescope) DR2 release \citep{luo2015}. The resulting 454,180 stellar data set contains infered $T_{eff}$, $log g$, $[Fe/H]$, and [$\alpha/M$] values.

\section{Analysis and Results}
\subsection{Line Selection}
\subsection{Technetium Lines}
\subsection{Abundance Analysis}
\subsection{Abundance Uncertainties}

>>>>

In our research we analysed 273 Barium canidates amoung the 454,180 stellar sample produced by \citet{ho2017} and with GAIA determined the galactic motions for 21 out the 273 canidates.

\section{Observations and Target Selection}
The spectral data of our stars were obtained from the \textit{Cannon} fits predictive model implemented by \citet{ho2017} on the LAMOST (Large Sky Area Multi-Object Fibre Spectroscopic Telescope) DR2 release \citep{luo2015}. The LAMOST spectral resolving power of R = 1800, a wavelength coverage from 3700$\AA$ to 9000$\AA$, and a nominal S/N ratio of 100. \citet{ho2017} cross-matches 9,952 stars between the low resolution spectra of LAMOST and the high resolution spectra from the APOGEE survey, and through a data driven spectral model. produces a 454,180 stellar data set. For this stellar data set the \textit{Cannon} predictive model infers $T_{eff}$, $log g$, $[Fe/H]$, and [$\alpha/M$] values.

The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}. A negative residual as shown in (I know I shoould expand here on the psoter child)figure \ref{fig:figure1} illustrates an enhancement in Ba\Rmnum{2} and Sr\Rmnum{2} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively. (thinking a sentence on why these lines are the strongest ?). The filter process had five requirements that each spectra for both enhancement lines had to meet to be considered a Barium star canidate, these included:

\renewcommand\labelenumi{(\roman{enumi})}
\renewcommand\theenumi\labelenumi

\begin{enumerate} 
\item Profile amplitude for both enhancement lines must exceed A$\leq$-0.05.
\item Both amplittudes must be measured within 3$\sigma$ $(|A|/\sigma _A \geq 3)$.
\item The wavelength at each absorption line must be within $2$\AA \hspace{0.2mm}$(\lambda \leq 2)$.
\item The chi must be less then 3 (not sure on math wrting for this).
\item And, the spectra must have a signal-to-noise ratio of S/N $\geq 30$.
\end{enumerate}
In addition, a visual observation of the accuracy between each normalised LAMOST flux and its accompanying data driven model was undertaken to exclude any results containing, false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra. This combined method generated the 273 Barium star candidates as listed in Table \ref{table:table1}.

\section{Analysis and Results}

\subsection{Line Selection}
\subsection{Technetium Lines}
\subsection{Abundance Analysis}
\subsection{Abundance Uncertainties}
